*italized text*
**BOLD**

## Secondary heading
### TErtiary heading

- first item
- second item
-third item

* first
* second

1. first
2. secon
3. third
5. fourh

[link](www.google.com)

or [link][1] random text

[1]: www.google.com "link"

newline require   
doule space


chunk of code, in R markdown print code and result
```{r}
set.seed(1)
x <- rnorm(100)
mean(x)
```

 in R markdown print only result
```{r , echo=FALSE}
set.seed(1)
x <- rnorm(100)
mean(x)
```

Show code only
```{r , results='hide'}
set.seed(1)
x <- rnorm(100)
mean(x)
```

 hide code chunk and result
```{r , echo=FALSE,results='hide'}
set.seed(1)
x <- rnorm(100)
mean(x)
```

### Inline text computations
```{r,echo=FALSE}
time <-format(Sys.time(),"%a %b %d %X %Y")
rand <- rnorm(1)
```
time is `r time` and number is `r rand`

plot
```{r, fig.height=4}
plot(cars)
```

###setting global setting
```{r , echo=FALSE}
#opts_chunk$set(echo=FALSE, results="hide")
#some error in above function
#cache=TRUE for caching results
```

 With some code chunks, we may not want the output generated by the chunk to be rendered into HTML but would prefer to print the output verbatim.
Set the option results = “asis”

For cacheing set option cache ="TRUE

```{r}
set.seed(1)
x <- rnorm(100)
mean(x)
```